---
title: "Global Plastics Production"
---

Global plastics production has increased over the past few decades. This data was pulled from "Ourworldindata.org", by Hannah Ritchie, Veronika Samborska and Max Roser. Then, the relevant data frames were joined to analyze the global plastics production over the years and forecast future production. Global plastics production has been increasing at a rapid pace.

```{r}
echo: FALSE
# Load necessary libraries
library(tidyverse)
library(tidyr)
library(dplyr)
library(readr)
```

```{r}
# Read the data
data <- "C:/Users/liuyu/Downloads/UsersdkaneDesktopprojects/plastic-pollution/1- global-plastics-production.csv" |>
  read_csv()

# Rename columns for easier access
colnames(data) <- c("Entity", "Code", "Year", "Production")
print(data)
```

```{r}
# Plot the data
p <- ggplot(data, aes(x = Year, y = Production)) +
  geom_point(color = 'blue', alpha = 0.6) +
  ggtitle("Yearly Plastic Production with Trendline and Forecast") +
  xlab("Year") +
  ylab("Production") +
  theme_minimal()

# Fit a model
model <- lm(Production ~ poly(Year, 2, raw = TRUE), data = data)

# Add the trendline to the plot
p <- p + geom_smooth(method = "lm", formula = y ~ poly(x, 2, raw = TRUE), se = FALSE, color = "red")

# Forecast future values
future_years <- data.frame(Year = seq(2020, 2030))
future_values <- predict(model, newdata = future_years)
future_data <- data.frame(Year = future_years$Year, Production = future_values)

# Add the forecast to the plot
p <- p + geom_line(data = future_data, aes(x = Year, y = Production), color = "red", linetype = "dashed")
```

```{r}
# Print the plot
print(p)
```

Global plastics production has increased over the past few decades. This data was pulled from "Ourworldindata.org", by Hannah Ritchie, Veronika Samborska and Max Roser. Then, the relevant data frames were joined to analyze the global plastics production over the years and forecast future production. Global plastics production has been increasing at a rapid pace.
